%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {WORTH Internet Systems} % Organization
    {The Hague, Netherlands} % Location
    {Jan. 2018 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {
          	  Project Kairos, digitization of the visa application process for the dutch ministry of foreign affairs.
   		  	  \newline
   		  	  Developed new features for the application.
   		  	  \newline
   		  	  Performed code reviews.
   		  	  \newline
 		  	  Documented technological decisions and best practices.
   		  	  \newline
   		  	  Set up the E2E testing project for our testers.
   		  	  \newline
   		  	  Set-up our build and release pipelines in Microsoft Azure.
   		  	  \newline
    		  Closely communicated with the designer and the client to identify the requirements for the application.
    		  \newline
  			  Technologies/Methodologies used: Angular, NGXS, BEM, Broadcast Channel API, pdf.js, Spectator, CodeceptJS, Spring, Hibernate, MySQL, Docker, Microsoft Azure.
     	  }
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Fullstack Developer} % Job title
{EagleScience Software} % Organization
{Amsterdam, Netherlands} % Location
{Apr. 2017 - Jan. 2018} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {\url{https://playtowork.nl/}}
			\newline
			Mainly developed the CMS for the android application PlayToWork, in which students play games and it matches them to job listings.
			\newline
			Technologies/Methodologies used: React, Redux, Cordova, GraphQL, Relay, PHP, Laravel, MySQL.  
		\item {\url{https://eaglescience.nl/?portfolio=digiz} 
			\newline
			Mainly developed the front-end for DIGIZ, a digitization of a method called GIZ which is a practical transparent means of bridging the communication between parents and children.
			\newline
			Technologies used: Angular, Cordova, Scala. }
		\item {\url{https://eaglescience.nl/?portfolio=neurostars}
			\newline
			Developed the initial workflow mainly using Scala for passing DICOM files through the different stages for the web application Neurostars.
			\newline
			Technologies used: Play, MySQL, Docker, Jenkins, Angular.}
	\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
